Manuscript

### 2015-04-29 inst/simulation/manuscript.Rmd
...

plotPopulationCorrelations <- function(populationCorrelations, case) {
  populationCorrelations$Scenario <- prettyScenario(populationCorrelations$Scenario)
  p <- ggplot(populationCorrelations, aes(True, Correlation)) + geom_point(size=1, colour="black") +
  facet_wrap(~Scenario, ncol=2) + xlab("True population size") +
  scale_y_continuous(limits=c(-1,1)) +
  #ggtitle(paste("Case:", case)) +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"),
                                      plot.title=element_text(size=10),
                                      plot.margin=unit(c(0, 0.2, 0, 0), units="line"),
                                      panel.margin=unit(0, units="line"))#, axis.text.x=element_text(angle=45, hjust=.5, vjust=1))
  return(p)
}

@@

plotCIProportions <- function(credibilityIntervals) {
  #modelLabels <- prettyModelName(unique(credibilityIntervals$modelName))
  credibilityIntervals$Model <- prettyModelName(credibilityIntervals$modelName)
  credibilityIntervals$CI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=Model, colour=CI)) +
    geom_hline(aes(yintercept=.5), color="grey90") +
    geom_hline(aes(yintercept=.95), color="grey90") +
    geom_point(aes(shape=Model, group=Model), position=position_dodge(width=.7)) +
    scale_shape_manual("Model", values=c(17,15,3)) +
    scale_colour_manual("CI", values=c("gray", "black")) +
    #scale_colour_manual("Model", values=c("blue", "green", "red"), labels=modelLabels) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion") + ylim(0, 1) +
    #facet_wrap(~panel) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
          plot.margin=unit(c(0.2, 0.2, 0, 0), units="line"),
          #legend.background=element_rect(fill="transparent"),
          legend.margin=unit(-2, units="line"),
          panel.margin=unit(0, units="line"),
          legend.position="bottom",
          legend.box="horizontal",
          legend.key.width=unit(.7, "line"))
  return(p)
}

>>>>

plotPopulationCorrelations <- function(populationCorrelations, case) {
  populationCorrelations$Scenario <- prettyScenario(populationCorrelations$Scenario)
  p <- ggplot(populationCorrelations, aes(True, Correlation)) +
    geom_hline(data=data.frame(y=0), aes(yintercept=y), color="darkgray") +
    geom_point(size=1, colour="black") +
    facet_wrap(~Scenario, ncol=2) + xlab("True population size") +
    scale_y_continuous(limits=c(-1,1)) +
    #ggtitle(paste("Case:", case)) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"),
                                        plot.title=element_text(size=10),
                                        plot.margin=unit(c(0, 0.2, 0, 0), units="line"),
                                        panel.margin=unit(0, units="line"))#, axis.text.x=element_text(angle=45, hjust=.5, vjust=1))
  return(p)
}

@@

plotCIProportions <- function(credibilityIntervals) {
  #modelLabels <- prettyModelName(unique(credibilityIntervals$modelName))
  credibilityIntervals$Model <- prettyModelName(credibilityIntervals$modelName)
  credibilityIntervals$CI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=Model, colour=CI)) +
    geom_hline(aes(yintercept=.5), color="darkgrey") +
    geom_hline(aes(yintercept=.95), color="darkgrey") +
    geom_point(aes(shape=Model, group=Model), position=position_dodge(width=.7)) +
    scale_shape_manual("Model", values=c(17,15,3)) +
    scale_colour_manual("CI", values=c("gray", "black")) +
    #scale_colour_manual("Model", values=c("blue", "green", "red"), labels=modelLabels) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion") + ylim(0, 1) +
    #facet_wrap(~panel) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
          plot.margin=unit(c(0.2, 0.2, 0, 0), units="line"),
          #legend.background=element_rect(fill="transparent"),
          legend.margin=unit(-2, units="line"),
          panel.margin=unit(0, units="line"),
          legend.position="bottom",
          legend.box="horizontal",
          legend.key.width=unit(.7, "line"))
  return(p)
}
